---
title: "Asistensi 2"
author: "Hans Cakrawangsa"
date: "2024-04-17"
output: html_document
---
```{r}
source("http://www.openintro.org/stat/data/cdc.R")
##Panggil data
cdc
```
```{r}
## nama
names(cdc)
```
## Exercise 1 
1. genhlth = categorical 
2. exerany = categorical
3. hlthplan = categorical
4. smoke100 = categorical
5. height = numerical 
6. weight = numerical
7. wtdesire = numerical
8. age = numerical
9. gender = numerical
## melihat data diambil dari barus awal
```{r}
head(cdc)
```

```{r}
head(cdc, n=100)
```
```{r}
tail(cdc)
```
## Summaries and table 
```{r}
summary(cdc)
```
```{r}
summary(cdc$weight)
```
## melihat statistik descriptive data 
```{r}
mean(cdc$weight)
var(cdc$weight)
## variance adalah distribusi angkanya misalnya dibandingkan dengan 1 3 5 6 7 dengan 10 20 50 60 70 maka variance yang besar adalah 10 20 50 60 70
median(cdc$weight)
```
## frekuensi pada kolom tertentu 
```{r}
table(cdc$smoke100)/20000
```
##memanggil dan memberi variable baru untuk menyimpan nilai
```{r}
smoke <- table(cdc$smoke100)/20000
```
##distribusi frekuensi relatif 
```{r}
smoke/20000
```
## Exercise 2 
1. Numerical Summary for Height 
```{r}
summary(cdc$height)
70-64
```
## 1st Quartile = 64.00
## 2nd Quartile = 67.00
## 3rd Quartile = 70.00 
IQR = 70-64 = 6

2. Numerical Summary for Age 
```{r}
summary(cdc$age)
57-31
```

## 1st Quartile = 31.00
## 2nd Quartile = 43.00
## 3rd Quartile = 57.00 
IQR = 57-31 = 26
3. Interquartile for gender
```{r}
summary(cdc$gender)
```
## Male Value = 9569
## Female value = 10431
4. Interquartile for exerany 
```{r}
summary(cdc$exerany)
```
```{r}
table(cdc$gender)/20000
```
```{r}
table(cdc$exerany)/20000
```
```{r}
table(cdc$gender)
```
```{r}
table(cdc$genhlth)/20000
```

##buat plot
```{r}
barplot(smoke)
```
## frekuensi sample yang merokok dan ga merokok berdasarkan gender
```{r}
table(cdc$gender,cdc$smoke100)
```
## buat plot
```{r}
mosaicplot(table(cdc$gender,cdc$smoke100), main = "Data Gender")
```
## Exercise 3 
1. Mosaic Plot reveal smoking habits and gender 
#rectangle mosaic plot who is smoke and isn't smoke between male and female

1. melihat nilai kolom ke-6 (weight) dari responden ke 567
```{r}
cdc[567,"weight"]
```
alternative
```{r}
cdc$weight[567]
```
##(2)melihat nilai kolom ke 6 (weight dengan n responden)
#contoh : data dari 10-20
```{r}
cdc[10:20,6]
```
## (3)melihat nilai data dari n responden
```{r}
cdc[10:20, ]
```
4) melihat nilai dari koloom ke 6 dari seluruh responden 
```{r}
cdc[,6]
```
## Alternatif lain 
```{r}
cdc$weight
```
# a little more on subsetting
## conditional commands
1. melihat kolom gender yang memiliki nilai "m"
```{r}
cdc$gender=="m"
```
2. melihat kolom age yang memiliki nilai lebih dari 30 
```{r}
cdc$age > 30
```
## subset data 
Subset (irisan)
```{r}
subset(cdc, cdc$gender == "m")
```
## several condition 
& dibaca "and" | dibaca " or"
##contoh subset 1
```{r}
m_and_over30 <- subset(cdc,cdc$gender=="m"& cdc$age>30)
m_and_over30
```
## contoh subset 2
```{r}
m_or_over30 <- subset(cdc,cdc$gender=="m"| cdc$age>30)
m_or_over30
```
##Exercise 4 
1. new object under 23 and smoke 
```{r}
under23_and_smoke <- subset(cdc,cdc$smoke100 & cdc$age<23)
summary(under23_and_smoke)
```

## box plot 
## quantitative data 
1. membuat plot untuk kolom height 
```{r}
boxplot(cdc$height)
```
## garis hitam = median
## box abu-abu = inter quartil (Q3-Q1)
## lingkaran kecil = sebacaran data yang terlalu ekstrem

2. membuat box plot berdasarkan gender 
```{r}
boxplot(cdc$height ~ cdc$gender)
```

3. membuat plot untuk bmi berdasarkan kolom genhlth
```{r}
bmi <- (cdc$weight/cdc$height^2) * 703
bmi
```
```{r}
boxplot(bmi ~ cdc$genhlth)
```
## Exercise 5 
1. What does the boxplot show? 
boxplot shown that the relational between body mass index and general health. 
2. relationship between categorical variable to bmi. 
- genhlth
```{r}
boxplot(bmi~cdc$genhlth)
```

- exenary
```{r}
boxplot(bmi~cdc$exerany)
```

- hlthplan
```{r}
boxplot(bmi~cdc$hlthplan)
```

-smoke100
```{r}
boxplot(bmi~cdc$smoke100)
```


4. membuat histogram dari kolom age 
```{r}
hist(cdc$age)
```
5. membuat histogram dari data bmi, dengan data dibagi menjadi 50 bin atau kelas
```{r}
hist(bmi,breaks = 50)
```
## On my Own
1. Make a scatterplot of weight versus desired weight. Describe the relationship between these two variables
```{r}
plot(cdc$weight~cdc$wtdesire)
```
2. Create this new variable by subtracting the two columns in the data frame and assigning them to a
new object called wdiff
```{r}
wdiff <- cdc$wtdesire - cdc$weight
wdiff
```
```{r}
str(wdiff)
```
3. What type of data is wdiff? If an observation wdiff is 0, what does this mean about the person’s weight and
desired weight. What if wdiff is positive or negative?
//wdiff is a numerical continous variable, if an observation wdiff is 0, it means the person's weight is exactly their desired weight (same weight)
// if the wdiff is positive : the person's desired weight is higher than the current weight (need gain weight)
// if the wdiff is negative : the person's desired weight is lower than the current weight (need lose weight)

4. Describe the distribution of wdiff in terms of its center, shape, and spread, including any plots you use.
What does this tell us about how people feel about their current weight?
//
```{r}
summary(wdiff)
```
boxplot below is not a normal distribution and has a few potential outliers. median is closer to the top of the box and the whisker is shorter on the upper end of the box the center below 0 and range is spread from -300 to 500     
```{r}
boxplot(wdiff)
```
```{r}
hist(wdiff, breaks = 30)
```
//this plot doesn't represent normal distribution. long tail of histogram plot is on negative direction on a number line. the mean lies toward left of median. from the summary of the data and hence it is negatively skewed distribution also known as left skewed distribution.
```{r}
plot(wdiff)
```

5. Using numerical summaries and a side-by-side box plot, determine if men tend to view their weight
differently than women.
```{r}
menweight <- subset(cdc,cdc$gender == "m")
menweight <- subset(cdc$wtdesire - cdc$weight, cdc$gender == "m")
womanweight <- subset(cdc$wtdesire - cdc$weight, cdc$gender == "f")
summary(menweight)
summary(womanweight)
```
```{r}
boxplot(menweight,womanweight)
```
//We can conclude that woman weight slightly bigger difference between their weight and desired weight than males by looking the summary (median & mean)  
6. Now it’s time to get creative. Find the mean and standard deviation of weight and determine what
proportion of the weights are within one standard deviation of the mean.
// 
```{r}
defsd <- subset(cdc$weight,cdc$weight > (mean(cdc$weight)- sd(cdc$weight)) & cdc$weight < (mean(cdc$weight)+ sd(cdc$weight)))
length(defsd)/nrow(cdc)
```
70.76% of the weight are within one standard deviation of the mean