---
title: "Asistensi 6"
author: "Hans Cakrawangsa"
date: "2024-05-29"
output: html_document
---
// Install library
```{r}
library(statsr)
library(dplyr)
library(ggplot2)
```

```{r}
download.file("http://www.openintro.org/stat/data/atheism.RData",
              destfile = "atheism.RData")
load("atheism.RData")
```
```{r}
head(atheism)
```
```{r}
View(atheism)
```

#United States data atheism and non atheism 
```{r}
us12 <- subset(atheism, nationality == "United States" & year == "2012")
us12
```
# Looking for US atheist proportion = 
# The COnclusion is there are 5% from overall US resident is atheist in 2012
```{r}
mean(us12$response == "atheist")
```
#Inference on Proportions
```{r}
inference(
  y = us12$response, 
  est = "proportion",
  type = "ci",
  method = "theoretical",
  succes = "atheist"
)
```
# Look for Error Margin = ZScore * SE (Standard Error from inference)
## Margin Eror is a measure how far our estimated sample from the truth value. So, if Margin Error is High, The Uncertainty is also High from the truth
```{r}
ME <- 1.96*0.0069
ME
```
# Looking for atheist proportion in US in the different year, 2005 and 2012
```{r}
usa <- subset(atheism, nationality == "United States" & year == "2012" | nationality == "United States" & year == "2005")
usa
```
```{r}
usa$year <- as.factor(usa$year)
inference(y = usa$response, x = usa$year, est = "proportion", type = "ci", method = "theoretical", success = "atheist")
```
Latihan Soal : 
1.With the inference functuions, calculate atheis proportion in 2012 in chinese and give the explanation
```{r}
china12 <- subset(atheism, nationality == "China" & year == "2012")
china12
```

```{r}
mean(china12$response == "atheist")
```
#Inference on Proportions
```{r}
inference(
  y = china12$response, 
  est = "proportion",
  type = "ci",
  method = "theoretical",
  succes = "atheist"
)
```
2. With the inference functions, calculate atheis proportion in 2012 in chinese and give the explanation 
```{r}
spain <- subset(atheism, nationality == "Spain" & year == "2012"| nationality == "Spain" & year == "2005")
spain
```
```{r}
mean(spain$response == "atheist")
```
#Inference on Proportions
```{r}
spain$year <- as.factor(spain$year)
inference(
  y = spain$response, 
  x = spain$year,
  est = "proportion",
  type = "ci",
  method = "theoretical",
  succes = "atheist"
)
```
3. Japan Atheist
```{r}
jap <- subset(atheism, nationality == "Japan" & year == "2012"| nationality == "Japan" & year == "2005")
jap
```
```{r}
mean(jap$response == "atheist")
```
#Inference on Proportions
```{r}
jap$year <- as.factor(jap$year)
inference(
  y = jap$response, 
  x = jap$year,
  est = "proportion",
  type = "ci",
  method = "theoretical",
  succes = "atheist"
)
```





