---
title: "Probability"
author: "Hans Cakrawangsa"
date: "2024-05-08"
output: html_document
---

## load data
```{r}
download.file("http://www.openintro.org/stat/data/kobe.RData",
              destfile = "kobe.RData")
load("kobe.Rdata")
head(kobe)
```
## Mengakses kolom basket elemen tertentu misal 1-10
```{r}
kobe$basket[1:9]
```
## Menghitung streaks dalam data basket 
```{r}
kobe_streak <- calc_streak(kobe$basket)
kobe_streak
```
#barplot
```{r}
barplot(table(kobe_streak))
```
#Pengambilan Sample acak pada pelemparan  koin
```{r}
outcomes <- c("Head","Tails")
sample(outcomes, size = 5, replace = TRUE)
```
True - Dengan pengembalian (Get Return)
False = Tanpa Pengembalian (Didn't Get Return)

## Fair 
```{r}
sim_fair_coin <- sample(outcomes, size = 100, replace = TRUE)
sim_fair_coin
```
```{r}
table(sim_fair_coin)
```
#Unfair 
```{r}
sim_unfair_coin <- sample(outcomes, size = 100, replace = TRUE, prob = c(0.2,0.8))
sim_unfair_coin
```
```{r}
table(sim_unfair_coin)
```
## Pengambilan sample acak pada basket
```{r}
outcomes <- c("H","M")
sim_basket <- sample(outcomes, size = 50, replace = TRUE)
sim_basket
```
Exercise 1 
Streak 1 = Awalnya shot masuk, terus nyoba lagi ga masuk
Streak 0 = Awalnya shot ga masuk, terus shot lagi ga masuk hahahah lol XD oakwoakwawk

Exercise 2
# Menambilkan BarPlot
```{r}
kobe_streak <- calc_streak(kobe$basket)
kobe_streak
barplot(table(kobe_streak))
```

# Mencari Frekuensi Terbanyak (modus) / Typical Streak
```{r}
streak_counts <- table(kobe_streak)
mode_streak_length <- as.numeric(names(which.max(streak_counts)))
print(paste("Kobe's typical streak length:", mode_streak_length))
```


# Mencari Streak Terbanyak (paling ujung di frekuensi sumbu x)
```{r}
longest_streak <- max(kobe_streak)
print(paste("Kobe's longest streak length:", longest_streak))
```


Exercise 3
# Pada unfair coin terdapat argumen prob(0.2,0.8)
```{r}
table(sim_unfair_coin)
```

Exercise 4 
```{r}
outcomes_shot <- c("H","M")
sim_basket <- sample(outcomes_shot, size = 133, replace = TRUE, prob = c(0.45,0.55))
sim_basket
table(sim_basket)
```
```{r}
barplot(table(sim_basket))
```
On My Own 

1. Describe the distribution of streak lengths. What is the typical streak length for this simulated independent
shooter with a 45% shooting percentage? How long is the player’s longest streak of baskets in 133 shots?
```{r}
calc_streak(sim_basket)
table(sim_basket)
```

2. If you were to run the simulation of the independent shooter a second time, how would you expect its streak
distribution to compare to the distribution from the question above? Exactly the same? Somewhat similar?
Totally different? Explain your reasoning
## its different because its a random sample 

3. How does Kobe Bryant’s distribution of streak lengths from page 2 compare to the distribution of streak
lengths for the simulated shooter? Using this comparison, do you have evidence that the hot hand model fits
Kobe’s shooting patterns? Explain

4. What concepts from the textbook are covered in this lab? What concepts, if any, are not covered in the
textbook? Have you seen these concepts elsewhere, e.g. lecture, discussion section, previous labs, or
homework problems? Be specific in your answer




