---
title: "Asistensi 3"
author: "Hans Cakrawangsa"
date: "2024-05-16"
output: html_document
---
// call data
```{r setup, include=FALSE}
download.file("http://www.openintro.org/stat/data/bdims.RData", destfile =
"bdims.RData")
load("bdims.RData")
```
//quick peek at the first row
```{r}
head(bdims)
```
## men dimension and female dimension
```{r}
mdims <- subset(bdims, bdims$sex == 1)
fdims <- subset(bdims, bdims$sex == 0)
mdims
fdims
```

Exercise 1 
## Histogram men dimensions and female dimensions
```{r}
hist(mdims$hgt)
hist(fdims$hgt)
```

## female height mean and female height standard deviation
```{r}
fhgtmean <- mean(fdims$hgt)
fhgtsd <- sd(fdims$hgt)
fhgtmean
fhgtsd
```

## 
```{r}
hist(fdims$hgt, probability = TRUE)
x <- 140:190
y <- dnorm(x=x, mean = fhgtmean, sd = fhgtsd)
lines(x=x, y=y, col = "blue")
```
Exercise 2 : 
##Based on the histogram, the data in histrogram is nearly follow the normal distribution line

#Quantile-Quantile female dimension height
```{r}
qqnorm(fdims$hgt)
qqline(fdims$hgt)
```
# Simulating data 
```{r}
sim_norm <- rnorm(n=length(fdims$hgt), mean = fhgtmean, sd = fhgtsd)
sim_norm
```
Exercise 3 
```{r}
sim_norm <- rnorm(n=length(fdims$hgt), mean = fhgtmean, sd = fhgtsd)
qqnorm(sim_norm, col = "blue")
qqline(sim_norm, col = "green")
```
## simulation qq norm
```{r}
qqnormsim(fdims$hgt)
```
Exercise 4 
## From the data above, the normal probability plot for fdims$hgt really look similiar to the plots from simulated data. 

Exercise 5 
## define men height 
```{r}
mhgtmean <- mean(mdims$hgt)
mhgtsd <- sd(mdims$hgt)

sim_norm <- rnorm(n=length(mdims$hgt), mean = mhgtmean, sd = mhgtsd)
qqnorm(sim_norm, col = "orange")
qqline(sim_norm, col= "brown")
```
```{r}
qqnormsim(mdims$hgt)
```
normally distributed

## normal probabilities
```{r}
1 - pnorm(q = 182, mean = fhgtmean, sd = fhgtsd)
```
## Assume normal distribution allowed to calculate theoritical probability
```{r}
sum(fdims$hgt>182) / length(fdims$hgt)
```
Exercise 6 
1. what is the probability the woman is shorter than 150 cm?
2. what is the probability the woman is  higher weight than  70kg?

##Shorter than 150 cm
```{r}
1 - pnorm(q = 150, mean = fhgtmean, sd = fhgtsd)
```
```{r}
sum(fdims$hgt<150) / length(fdims$hgt)
```
## Weight higher than 70kg
```{r}
fwgtmean <- mean(fdims$wgt)
fwgtsd <- sd(fdims$wgt)
pnorm(q = 70, mean = fwgtmean, sd = fwgtsd)
```
```{r}
sum(fdims$hgt>70) / length(fdims$hgt)
```
```{r}
qqnorm(fdims$che.di)
qqline(fdims$che.di)
```
# On Your Own
1.Now let’s consider some of the other variables in the body dimensions data set. Using the figures on the
next page, match the histogram to its normal probability plot. All of the variables have been standardized
(first subtract the mean, then divide by the standard deviation), so the units won’t be of any help. If you are
uncertain based on these figures, generate the plots in R to check.

A. The histogram for female biiliac (pelvic) diameter (bii.di) belongs to normal probability plot letter _B_.

```{r}
hist(fdims$bii.di, probability = TRUE)
qqnorm(fdims$bii.di)
qqline(fdims$bii.di)
```
B. The histogram for female elbow diameter (elb.di) belongs to normal probability plot letter _C_.
```{r}
hist(fdims$elb.di, probability = TRUE)
qqnorm(fdims$elb.di)
qqline(fdims$elb.di)
```
C. The histogram for general age (age) belongs to normal probability plot letter _D_.
```{r}
hist(fdims$age, probability = TRUE)
qqnorm(fdims$age)
qqline(fdims$age)
```
D. The histogram for female chest depth (che.de) belongs to normal probability plot letter _A_.
```{r}
hist(fdims$che.de, probability = TRUE)
qqnorm(fdims$che.de)
qqline(fdims$che.de)
```
2. Note that normal probability plots C and D have a slight stepwise pattern. Why do you think this is the
case?
## There are Slight stepwise pattern because of repeated values and rounding up of values like "age" as a example. 

3. As you can see, normal probability plots can be used both to assess normality and visualize skewness.
Make a normal probability plot for female knee diameter (kne.di). Based on this normal probability plot, is
this variable left skewed, symmetric, or right skewed? Use a histogram to confirm your findings.
```{r}
qqnorm(fdims$kne.di)
qqline(fdims$kne.di)
```
```{r}
fknedimean <- mean(fdims$kne.di)
fknedisd <- sd(fdims$kne.di)
fknedimean
fknedisd
```
## CHECK SKEWED
```{r}
hist(fdims$kne.di, probability = TRUE)
x <- 14:26
y <- dnorm(x=x, mean = fknedimean, sd = fknedisd)
lines(x = x, y = y, col = "black")
```
## THE ANSWER IS SKEWED TO RIGHT OR RIGHT SKEWED. 
4. What concepts from the textbook are covered in this lab? What concepts, if any, are not covered in the
textbook? Have you seen these concepts elsewhere, e.g. lecture, discussion section, previous labs, or
homework problems? 
## Concepts : 
1. Normal Distributions
2. Normal Distributions Probability
3. Evaluating Normal Distributions
4. Normal Probabilities (with substract mean and standard deviation)







